\chapter{Welcome}

Welcome to the Book of Abstracts for the 42nd International Conference on Mathematical Methods in Economics (MME 2024)! We are delighted to present this compilation of selected contributions from researchers and practitioners in the field of economics and mathematical modeling.

MME 2024 continues the tradition of fostering intellectual exchange and collaboration among academicians, professionals, and students interested in the theory and application of mathematical methods in economics. This year's conference, hosted by the the Department of Computer Science, Faculty of Science, Jan Evangelista Purkyně University in Ústí nad Labem, promises to be a vibrant platform for sharing cutting-edge research, innovative methodologies, and practical insights.

Within this book, you will find abstracts of the presentations scheduled for the conference. These abstracts offer concise yet informative summaries of the topics that each presenter will explore, providing a glimpse into the breadth and depth of research being conducted in the field.

We extend our heartfelt gratitude to all the authors who have contributed their work to this volume, as well as to the organizers, reviewers, Czech Society for Operations Research, and members of the scientific committee for their invaluable contributions to the success of MME 2024.

We also wish to express our sincere appreciation to our distinguished plenary speakers, Prof. Panos M. Pardalos from the University of Florida, USA, and Prof. Michal Černý from the Prague University of Economics and Business, Czech Republic. Their expertise and insights will undoubtedly enrich the conference program and inspire attendees to push the boundaries of knowledge in mathematical methods applied to economics.

As we embark on this intellectual journey together, we hope that MME 2024 will serve as a catalyst for fruitful discussions, new collaborations, and advancements in the field of mathematical economics.

General Chair of MME 2024

Hossein Moosaei, Jan Evangelista Purkyně University, Czech Republic

