\hlavka{ The Problem of Optimal Delivery of Frozen and Chilled Goods with given priority from Multiple Warehouses }{ Jaromír Zahrádka }{ jaromir.zahradka@upce.cz }{ University of Pardubice, Czechia }{  }

\begin{Abstrakt}
    This article comes up with a specific example of the truck routing problem. The selling company has to deliver the ordered frozen or chilled goods from m warehouses to n customers as efficiently as possible. Each customer has ordered goods stored in a certain number of containers which need to be transported. All customer points of delivery and warehouse points are given by GPS coordinates. The objective of the solution is to select the number of vehicles and their routes between suitable warehouse and customers in such a way that the total travel distance or travel time is as short as possible. The order of customers on each route respects the priority of delivery of frozen goods over chilled ones. This means that chilled goods are unloaded from the truck only after all frozen goods have been unloaded at previous customer delivery points. Each of these delivery points is visited only once by one of the vehicles. In each warehouse, the same number of trucks ends the journey as they left. All trucks have the same pre-limited capacity of containers. In this article, the algorithm of the truck routing problem with multiple warehouses and priority of de-livery of frozen goods was created and implemented in Matlab code.
\end{Abstrakt}

\klicovaslova{
    Goods, Matlab, Mixed integer linear programming, Optimization, Priority, Truck routing problem
}


\clearpage