\hlavka{ Global optimization problem in max-plus algebra }{ Helena Myšková }{ helena.myskova@tuke.sk }{ Technical University of Košice, Slovakia }{  }

\begin{Abstrakt}
    The behavior of discrete-event systems, in which individual components move from event to event, rather than varying smoothly in time, is often described using max-plus algebra. Max-plus linear systems whose basic operations are maximization and addition can be used to describe a class of dynamical systems with synchronization but no concurrency or choice, although such systems are generally nonlinear in conventional algebra. Applications of max-plus linear systems arise in the context of manufacturing plants, traffic management, high-performance screening systems, etc. Global optimization is an optimal control problem that finds the global minimum or maximum of a function or set of functions over a given set. The growing interest in global optimization for max-plus linear systems is related to its importance in both theory and applications. Consider the global optimization problem of minimizing the max-plus product $A.x$, where $A$ is a given matrix and the constraint set is the set of column vectors $x$ such that the sum of $k_j.x_j$ is equal to $c$, where $c$ is a given positive real constant and $k_j$ are non-negative numbers with sum equal to 1. We will show that the solvability of a given global optimization problem is independent of the number $c$ if the components of the vector $x$ can be also negative. From a practical point of view, we further consider the solvability of the global optimization problem with non-negative constraints. We will propose an algorithm to find the set of all values of $c$ for which the problem is solvable. We will show the practical importance of the load distribution task, which focuses on a reasonable and transparent redistribution of the system load between processors in order to optimize the overall system performance.
\end{Abstrakt}

\klicovaslova{
    max-plus algebra, max-plus linear model, constraint function, global optimization, application in distributed system
}


\clearpage